Using tours to visually investigate properties of new projection pursuit indexes with application to problems in physics

### 2019-12-18 scagnostics.Rmd
Fixed references.

bibliography: bibliography.bib
output: rticles::springer_article
header-includes:
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{amsmath}
  - \usepackage{amssymb}
  - \usepackage{xcolor}
  - \usepackage{bm}
---

>>>>

bibliography: [bibliography.bib]
output: rticles::springer_article
header-includes:
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{amsmath}
  - \usepackage{amssymb}
  - \usepackage{xcolor}
  - \usepackage{bm}
---
